Nodal Discontinuous Galerkin Method for the Two-Moment Model of Neutrino Transport

### 2017-04-03 Documents/M1/dgM1Curvilinear.tex
Adding figures for transport problems

@@

@@

\begin{table}
  \caption{Parameters for homogeneous sphere problem with tabulated opacities.}
  \begin{tabular}{ccccc}
    Model & $\rho$ [g~cm$^{-3}$] & $T$ [MeV] & $Y_{e}$ & $\mu_{\nu}$ [MeV] \\
    \midrule \midrule
    A & $1.0\times10^{14}$ & 21.0  & 0.25 &   90.65 \\
    B & $1.0\times10^{13}$ & 16.0 & 0.14 &     4.80 \\
    C & $1.0\times10^{12}$ &   8.0 & 0.12 & -   0.57 \\
    D & $1.0\times10^{11}$ &   8.0 & 0.15 & - 10.87 \\
    \midrule \midrule
  \end{tabular}
\end{table}

@@

>>>>

\ee{Ran write about tabulated B85 absorption and scattering opacities.}

@@

\begin{table}
  \caption{Parameters used for problems with tabulated opacities. \label{tab:tabulatedModels}}
  \begin{tabular}{ccccc}
    Model & $\rho$ [g~cm$^{-3}$] & $T$ [MeV] & $Y_{e}$ & $\mu_{\nu}$ [MeV] \\
    \midrule \midrule
    A & $1.0\times10^{14}$ & 21.0  & 0.25 &   90.65 \\
    B & $1.0\times10^{13}$ & 16.0 & 0.14 &     4.80 \\
    C & $1.0\times10^{12}$ &   8.0 & 0.12 & -   0.57 \\
    D & $1.0\times10^{11}$ &   8.0 & 0.15 & - 10.87 \\
    \midrule \midrule
  \end{tabular}
\end{table}

@@

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}
      \includegraphics[scale=0.4]{./Figures/HomogeneousSphere_Opacities} &
      \includegraphics[scale=0.4]{./Figures/HomogeneousSphere_BaseSpectra} \\
      \includegraphics[scale=0.4]{./Figures/HomogeneousSphere_VsRadius_B} &
      \includegraphics[scale=0.4]{./Figures/HomogeneousSphere_VsRadius_D}
    \end{tabular}
  \end{center}
  \caption{Results from solving the multi-group Homogeneous sphere problem with the DG(1)+SIRK2 method using $100$ elements.
    In the upper left panel we plot the absorption opacity versus energy $\epsilonNu$ using the values for $\rho$, $T$, and $Y_{e}$ listed in Table~\ref{tab:tabulatedModels}. In the upper right panel, we plot the spectral number density versus energy at the end of the computations for a radius of $52.5$~km solid lines.  The corresponding Fermi-Dirac spectrum is also plotted (dashed lines).  }
  \label{fig:homogeneousSphere1D_weaklib}
\end{figure}

@@

We conclude with a problem mimicking the deleptonization of a collapsed stellar core.  
To this end, we adopt an analytic density profile
\begin{equation}
  \rho(r)=\big[\,1-\Theta(r)\,\big]\,\rho_{1}(r)+\Theta(r)\,\rho_{2}(r)
  \label{eq:densityProfile}
\end{equation}
where the function $\Theta(r)=0.5\times\big[\,1.0+\tanh\big(\,(r-r_{0})/R_{0}\,\big)\,\big]$ transitions smoothly between two density profiles, given by a Gaussian in the central region and a polynomial at larger radii; i.e.,
\begin{align}
  \rho_{1}(r)
  &=\rho_{1,0}\times\exp\big[-(r/R_{1})^{2}\big]
  \label{eq:densityProfile1} \\
  \rho_{2}(r)
  &=\rho_{2,0}\times\big(r/R_{2}\big)^{\alpha},
  \label{eq:densityProfile2}
\end{align}
where $\rho_{1,0}>\rho_{2,0}$ and $\alpha<0$.  
We set $\rho_{1,0}=4.5\times10^{14}$, $\rho_{1,0}=1.0\times10^{13}$, $\alpha=-4$, and $R_{1}=10$~km.  
Then, by imposing $\rho_{1}(R_{2})=\rho_{2}(R_{2})$, we find $R_{2}=R_{1}\sqrt{\ln(\rho_{1,0}/\rho_{2,0})}\approx19.5$~km.  
We also set $r_{0}=R_{2}$ and $R_{0}=1$~km.  
With these parameters, the density profile given by Eqs~\eqref{eq:densityProfile}, \eqref{eq:densityProfile1}, and \eqref{eq:densityProfile2} provides a reasonable approximation to the density profile in the post-bounce phase of a supernova realistic model (cf. Figure~\ref{fig:analyticDensityProfile}).

\begin{figure}
  \begin{center}
      \includegraphics[scale=0.5]{./Figures/AnalyticDensityProfile}
  \end{center}
  \caption{Density profile used in the deleptonization problem (solid black line; cf. Eq.~\eqref{eq:densityProfile}).  
  It is composed of a Gaussian profile for radii $\lesssim20$~km (dashed black line), and a power law, with $\rho\propto r^{-4}$, for larger radii (dotted black line).  
  The density profile from a full physics core-collapse supernova simulation at $100$~ms after core bounce is also plotted (solid red line).  }
  \label{fig:analyticDensityProfile}
\end{figure}
